\documentclass{article}
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{graphicx}
  \usepackage{float}
  \usepackage{setspace}
  \usepackage{stata}
  \usepackage{color}
    \definecolor{gray}{rgb}{0.2,0.2,0.2}
    \definecolor{Blue}{RGB}{0,0,255}
    \definecolor{NavyBlue}{RGB}{0,0,128}
    \definecolor{Maroon}{RGB}{128,0,0}
    \definecolor{TealBlue}{RGB}{0,128,128}
    \definecolor{OliveGreen}{RGB}{0,128,0}
  \usepackage{bm}
  \usepackage{amssymb}
  \usepackage{listings}
  \usepackage[colorlinks, linkcolor=NavyBlue, anchorcolor=Maroon, citecolor=TealBlue]{hyperref}%For hyper-link reference
  \input{Stata.tex}% for stata language highlights
\topmargin=-1.2cm \oddsidemargin=0.1cm \evensidemargin=0.1cm
\textwidth=16 true cm \textheight=23 true cm

\font\euler=EUSM10 \font\eulers=EUSM7

\begin{document}
\title{Updates on Academic and Professional Activities\\Jan 2014 - Jan 2015}
\author{{\normalsize SHENG Hao}}
\date{\today}

\maketitle

\def \Pr{{\rm Pr}}
\baselineskip 0.6cm
\section{Research Projects}
\subsection{Undergraduate Thesis: Starburst Migration and Technology Diffusion}
\begin{description}
\item[Advisor:] \href{http://wulemin.weebly.com/index.html}{Prof. Lemin WU}. 
\item[Fields:] Economic History
\item[Abstract:] This paper shows how migration responds to technology shock in a historical context. Historical migrations appear lack of common laws because there are actually four types of them, which we distinguish along two dimensions, i.e. whether the migration is to equilibrium or in equilibrium, and whether technology diffuses along with migration. We model each type of migration and explain the direction, distance and duration of a wide range of migration events, including the exodus out of Africa, the spread of Neolithic culture, and pre-modern European rural-urban migration. {\it \href{http://shenghao.weebly.com/uploads/2/4/2/1/24218782/writingsample2migration_shenghao.pdf}{Fulltext}}\\

\end{description}

\subsection{Leadership and Political Selection}
This project is led by \href{http://en.nsd.edu.cn/article.asp?articleid=6962}{Prof. Yang Yao} and \href{http://www.xitianyang.com}{Prof. Tianyang Xi}. We construct a dataset covering the personal characters of world political leaders, and start to do some empirical research on it.
\begin{description}
\item[Fields:] Political Economy
\item[Dataset Coverage:] The data set is intended to cover all countries that were or would become independent at any time after 1917, each from the inception of the first representative institutions or from the date of independence, whichever comes first, through 2010.
\item[Codebook and Coding Notes:] \href{http://shenghao.weebly.com/uploads/2/4/2/1/24218782/leaderships_and_political_selection-codebook.pdf}{Codebook}, \href{http://shenghao.weebly.com/uploads/2/4/2/1/24218782/notesofupdate.pdf}{Notes}
\item[Introductory Slides:] \href{http://shenghao.weebly.com/uploads/2/4/2/1/24218782/leadership_1950-2010-patterns.pdf}{Slides}
\item[GitHub Repository:] \url{https://github.com/Hari-Sheng/Leadership}
\end{description}


\subsubsection{Proposal under this project}
\begin{description}
\item[TV and Leaders:] We are interested in the rationality of voters(upon leaders' age and appearance) and will use the exogenous shock of media's introduction(e.g. TV).
\item[Bonds and Leaders:] We are interested in the relation between the rank of sovereign funds and corresponding leaders' personal characters.
% \item[Replication of (Acemoglu, 2014B)]: \href{http://shenghao.weebly.com/uploads/2/4/2/1/24218782/democracy_and_growth.pdf} {Notes}
\end{description}
\subsection{Update of Visa Policy Project(Writing Sample Submitted Last Year)}


\newpage
\section{Professional Projects}
Most of the Projects at \href{http://thcapital-china.com/}{T.H.Capital, LLC} are done from June to December. T.H. Capital is an independent research and investment advisory firm specializing in China. It offers real-time, on-the-ground, bottom-up research across a wide spectrum from macro and industry analysis to company specific projects; from China ADRs to international names that have meaningful exposure to China market. \\
My responsibility mainly lies in two field: 1) processing data collected by computer engineer and support analysis; 2)Develop new products.


\subsection{Report and DataFlash}
Report is a formal ranking of a specific firm which gives a ranking of sell, hold and buy and a target price. It's usually released quarterly.\\
DataFlash is a data-based summary of operating metrics. It is updated on a daily basis. And is available on request for registered customers.
\begin{description}
\item [Covering Companies:] NOAH, WUBA, VIPS, BABA(NYSE); TOUR, BONA, JD(NASDAQ) 
\item [Public Reports:] \url{http://thcapital-china.com/content/type/data}
\item [GitHub:] \url{https://github.com/Hari-Sheng/T.H.Capital}
\end{description}
\subsection{Advertising in the Online Videos}
This project aims to cover 90\% of China online video advertiser since advertising expense is leading indicator for FMCG(fast-moving consumer goods). Major China video platform like Youku(NYSE:YOKU) and Sohu(NASDAQ:SOHU), etc. are real time monitored by our programs. 

\newpage
\section{Coding and Data-oriented Work}
\subsection{Stata Syntax Highlighting in \LaTeX}	
The following is an template:
\lstinputlisting[language=stata, style=stata-editor]{AFE2014Fa2.txt}
More details could be reached at GitHub:
\subsection{SogouIndex}
Sogou is a popular SE(search engine) in China (with a market share of 10\%). Just as Google Trends and BaiduIndex, SogouIndex tries to measure popularity of given keywords based on the searching behavior of its users. This program will download SogouIndex automatically for given keywords, and stored them in .xlsx files.

The demo of this program is done during my internship at T.H.Capital, Jul. 2014. We are using searching indexes to predict the sale volume of upcoming cellphone, the numbers of visitors to Macau, etc. 

More details could be reached at GitHub: \url{https://github.com/Hari-Sheng/SogouIndex}

\subsection{SAC(Security Associate of China) Public Data}
The personal information and professional experience of registered SAC members are public data which has more than 200 thousand records\footnote{\url{http://person.sac.net.cn/pages/registration/sac-publicity-report.html}}. I am now constructing this database for further works.

\newpage
\section{Other Information}
\subsection{Part-time Course-load and Free Mover Plan}
\subsubsection{Guanghua School of Management(GSM), Peking University}
In my part-time, I finish several graduate courses at GSM:
\begin{description}
\item[Advanced Microeconomics] Textbook: MWG; Lecturer: \href{https://ideas.repec.org/f/pme419.html}{Juanjuan Meng}\footnote{2005-2010 Ph.D in Economics, UCSD}
\item[Advanced Financial Econometrics] Textbook: Lecture notes; Lecturer: Yaping Wang
\item[Advanced Finance I, II] Textbook: Lecture notes; Lecturer: \href{https://ideas.repec.org/f/plu286.html}{Ruichang Lu}
\end{description}
Transcripts could be provided if needed.

\subsubsection{Free mover at HEC Paris, from Jan 2015 to May 2015}
I will stay at HEC Paris as a free mover, learning French and getting exposure to finance and management topics.
\quad\\

\subsection{Language}
\subsubsection{French}
I took 150-200 hours' French course at \href{http://www.alliancefr.org/}{Alliance Française, Beijing} since Oct 2014: approximately an equivalent to A2-level(basic communicating).
\quad\\
\subsection{Recent Standard Tests\protect\footnote{Reports have been sent from ETS}}
\begin{description}
\item[TOEFL(Nov. 9, 2014):] 108. Reading-29; Listening-28; Speaking-23; Writing-28
\item[GRE(Oct. 12, 2014):] 165(95\%) in Verbal Reasoning, 170(98\%) in Quantitative Reasoning
\item[GRE Math-Sub(Oct. 25, 2014):] 820(83\%)
% \item[SAC(Mar 2014):] Certificate Of Security Qualification, issued by Securities Association of China(SAC), ID: 20131011804524011
% \item[CFA(Dec. 6, 2014, {\it In Progress}):] Chartered Financial Analyst, Level I 
\end{description}
% \begin{appendix}
% \section*{Appendix}
% \lstinputlisting[language=mathematica]{Q4plot.nb}
% \end{appendix}
\quad\\
% \section{Update of Reference Letter}
% {\it In the next Page}
\end{document}
